full title

### 2020-11-18 paper/pldi21/implementation.tex
Replaced a paragraph in implementation.

\paragraph{Abstract Locations for Objects.}
During dynamic analysis, each JavaScript object should be designated by the
corresponding abstract location used in the static analysis.  In this paper, we
define abstract locations using the allocation site
abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
each abstract context in the static analyzer.  Thus, we instrument the given
JavaScript program to annotate each object created during dynamic analysis with
its allocation site and context information.  After the sealed symbolic
execution, the dynamic analyzer collects the objects based on their annotated
information for each abstract location.

@@

>>>>

\paragraph{Synchronization of Control Points.}
For seamless interactions between the static analyzer and dynamic shortcuts,
the synchronization of control points is a prerequisite.
The static analyzer compiles a target JavaScript program to intermediate
representation and builds a control flow graph.  It produces annotations for
control points on the CFG including functions, call sites, and object allocation
sites.  During the sealed symbolic execution, the dynamic analyzer requires
those annotations to calculate sensitive location names of newly created object
and lexical environments.  The key to place annotations on the instrumented code
is the span information of the original AST node.  Both the CFG of SAFE and
instrumented code of Jalangi maintain the span information, but they use
different parsers resulting mismatches for some corner cases.  Thus, we
preprocess to synchronize control points of two analyzers by the closest match
of the span information rather than the exact match.

@@

%\paragraph{Abstract Locations for Objects.}
%During dynamic analysis, each JavaScript object should be designated by the
%corresponding abstract location used in the static analysis.  In this paper, we
%define abstract locations using the allocation site
%abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
%each abstract context in the static analyzer.  Thus, we instrument the given
%JavaScript program to annotate each object created during dynamic analysis with
%its allocation site and context information.  After the sealed symbolic
%execution, the dynamic analyzer collects the objects based on their annotated
%information for each abstract location.
